---
title: "Student Surveys for Online Courses"
bibliography: library.bib
biblio-style: apalike
---

```{r, child="_setup.Rmd"}
```

# Abstract
I would like to develop a project that can take new survey data each term (either directly from Qualtrics via an API or from downloaded .csv files) and quickly create a report. Portions of this project would include
1. A process to import and clean the data each term.
2. One or more standard visualizations of Likert-type item data.
3. Organization and/or parsing of open-ended text responses.
4. Report Template

# Introduction

# Literature Review

# Methodology

## Data
Loading Packages
```{r}
library(tidyverse)
library(readr)
```
Using Dummy Data
```{r}
AAA_111 <- read_csv("survey_project/data/AAA_111_Survey_Responses.csv")
AAA_112 <- read_csv("survey_project/data/AAA_112_Survey_Responses.csv")
AAA_111_no_hd <- AAA_111[-c(1,2), ]
AAA_112_no_hd <- AAA_112[-c(1,2), ]
all_surveys <- rbind(AAA_111_no_hd,AAA_112_no_hd)
all_likert <- all_surveys[ , -c(1:8, 10:17, 22, 29:38, 47, 49, 51, 53, 55, 57, 59, 61, 64:86)]
all_likert <- gather(all_likert, key = "Question", value = "Response", -ResponseId)
```

## Analysis

# Results

# Discussion

# Conclusion

# References
